20200128_InsideSherpa_Task1_DraftSolutions - Template (1).Rmd
---
title: "Quantium Virtual Internship - Retail Strategy and Analytics - Task 1"
mainfont: Roboto
monofont: Consolas
output:
 pdf_document:
 df_print: default
 highlight: tango
 keep_tex: yes
 latex_engine: xelatex
header-includes:
 \usepackage{fvextra}

\DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,commandchars=\\\{\}}
---
```{r setup, include=FALSE}
# set options for R markdown knitting
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(linewidth=80)
```
```{r knitr line wrap setup, include=FALSE}
# set up line wrapping in MD knit output
library(knitr)
hook_output = knit_hooks$get("output")
knit_hooks$set(output = function(x, options)
{
 # this hook is used only when the linewidth option is not NULL
 if (!is.null(n <- options$linewidth))
 {
 x = knitr:::split_lines(x)
 # any lines wider than n should be wrapped
 if (any(nchar(x) > n))
 x = strwrap(x, width = n)
 x = paste(x, collapse = "\n")
 }
 hook_output(x, options)
})
```
# Task 1
Below is my report for the analysis of Julia's data.

## Data Checks
Note that you will need to install these libraries if you have never used these
before.

```{r 0 Load Libraries, results = 'hide'}
library(data.table)
library(ggplot2)
library(ggmosaic)
library(readr)
library(readxl)
filePath <- ""
transactionData <- read_excel("QVI_transaction_data.xlsx", sheet = "in")
customerData <- fread(paste0(filePath,"QVI_purchase_behaviour.csv"))
```

```{r Examining transaction data}
#### Examine transaction data
str(transactionData)
# We can see that all columns are in reasonable formats for analysis except for DATE. From online research, this form on Windows represents the number of days from the date 1899-12-30

# Map date column to R date object
transactionData$DATE <- as.Date(transactionData$DATE , origin = "1899-12-30")

# Verify transformed date column
str(transactionData)

```


